% thesisresults.tex
% Chapter Results.

% Results
\chapter{Results}
\label{cha:results}
The benchmark configurations, as described in section \ref{sec:methodologyexperiment_benchmarking}, having been executed on the platforms, as described in section \ref{sec:methodologyexperiment_platformconfiguration}, using the profiling methods described in section \ref{sec:methodologyexperiment_platformprofiling}, are presented in this chapter.
As such, the results gathered from execution on the \dvttermhost\ is presented in figure \ref{fig:histogramshost}, the results compiled from execution in the \dvttermandroidemulator\ are presented in figure \ref{fig:histogramsqemu}, and the results accumulated from software rasterized- and paravirtualized execution in \dvttermsimics\ are presented in figures \ref{fig:histogramssimicsparachess}, \ref{fig:histogramssimicsparajulia}, and \ref{fig:histogramssimicsparaphong}, respectively.
See section \ref{sec:histograms} for an elaboration on how the data is visualized in the referenced graphs.

% TODO:
% Below yadda yadda is visualized in histograms (see section Histograms for an elaboration on how these ought be interpreted).

% TODO:
% QEMU performance
% X11 Performance
% X11 complete performance under appendix or results?
% Magic instruction profiling
% Section for each demo? (analysis, rather?)

% hosthistograms
\input{fighistogramshost.tex}

% qemuhistograms
\input{fighistogramsqemu.tex}

% simicsparachesshistograms
\input{fighistogramssimicsparachess.tex}

% simicsparajuliahistograms
\input{fighistogramssimicsparajulia.tex}

% simicsparaphonghistograms
\input{fighistogramssimicsparaphong.tex}

% Histograms
\section{Histograms}
\label{sec:histograms}
The benchmarking results gathered for the purposes of this study, with the profiling methods having been described in section \dvtcmdrefname{sec:methodologyexperiment_platformprofiling}, are compiled into histograms; visualizing elapsed time in milliseconds to density in the figures presented in this section.
As such, the $Y$ axis showcases sample density; although the axis keys have been removed as they bear little relevance to the outcomes presented in this document.
The histograms each feature \dvtcmdnum{100} bins based off the \dvtcmdnum{1000} samples gathered per benchmark, as described in section \dvtcmdrefname{sec:methodologyexperiment_platformprofiling}, which are rounded into said bins.
For the purposes of good visualization methodology, values outside of the standard deviation\footnote{That is; values above that of the $mean + std$ and values under that of $mean - std$.} are not featured in the figures presented in this section.
In order to accomodate for the, however few, samples outside of said limits the figures are all complemented with key ratio tables (see tables \ref{tab:keyvalhost}, \ref{tab:keyvalqemu}, \ref{tab:keyvalsimics}, and \ref{tab:keyvalpara}, respectively).

\input{tabkeyvalhost.tex}
\input{tabkeyvalqemu.tex}
\input{tabkeyvalsimics.tex}
\input{tabkeyvalpara.tex}